### 2022-07-25 src/text/2-package.tex
Adapt sub-package descriptiosn to use code shortcut
Update package overview section

\section{Analysis Workflow Overview}
\label{sec:analysis-workflow-overview}

% This might not be the bast place compared to introduction
The data processing workflow in Gamma-ray astronomy is usually split in two sequences.
The first one deals with the data processing from camera measurement, calibration, event
reconstruction and selection to yield a list of reconstructed gamma-ray event candidates.
This sequence, sometimes referred to as low-level analysis, is usually very specific to
a given observation technique and even to a given instrument.

@@

\section{Gammapy package}
\label{sec:gammapy-package}

\subsection{Overview}
\label{ssec:overview}
The \gammapy package is structured into multiple sub-packages. The definition
of the content of the different sub-packages follows mostly the stages in the
data reduction workflow described in the previous section. Sub-packages
either contain data structures representing data at different data reduction
levels or contain algorithms to transition between the different data reduction
levels.

Figure~\ref{fig:data_flow} shows an overview of the different sub-packages and
their relation to each other. The \code{gammapy.data} and \code{gammapy.irf}
sub-packages define data objects to represent DL3 data, such as
event lists and instrument response functions as well as functionality
to the DL3 data from disk into memory.

The \code{gammapy.makers} sub-package contains the functionality to reduce
the data to binned maps.

\begin{figure*}[t]
	\centering
	\includegraphics[width=1.\textwidth]{figures/data_flow.pdf}
	\caption{
		Gammapy sub-package structure and data analysis workflow. The top row
        defines the groups for the different data levels and reduction steps
        from raw gamma-like events on the left, to high level science products
        on the right. The direction of the data flow is illustrated with the
        grey circles. The gray folder icons represent the different sub-packages
        in Gammapy and their names. Below each icon there is an overview of the most
        important objects defined in the sub-package.
    }
	\label{fig:data_flow} \end{figure*}

\input{text/2-package-subsections/data}
\input{text/2-package-subsections/irf}
\input{text/2-package-subsections/maps}
\input{text/2-package-subsections/makers}
\input{text/2-package-subsections/datasets}
\input{text/2-package-subsections/modeling}
\input{text/2-package-subsections/stats}
\input{text/2-package-subsections/estimators}
\input{text/2-package-subsections/analysis}
\input{text/2-package-subsections/visualisation}
\input{text/2-package-subsections/astro}
\input{text/2-package-subsections/catalog}
\input{text/2-package-subsections/utils}

>>>>

\section{Gamma-ray Data Analysis}
\label{sec:gamma-ray-data-analysis}

% This might not be the bast place compared to introduction
The data reduction process in \gammaray astronomy is usually split into two parts.
The first one deals with the data processing from camera measurement, calibration, event
reconstruction and selection to yield a list of reconstructed \gammaray event candidates.
This sequence, sometimes referred to as low-level analysis, is usually very specific to
a given observation technique and even to a given instrument.

@@

\section{Gammapy Package}
\label{sec:gammapy-package}
\subsection{Overview}
\label{ssec:overview}
%
\begin{figure*}[ht!]
	\centering
	\includegraphics[width=1.\textwidth]{figures/data_flow.pdf}
	\caption{
		Gammapy sub-package structure and data analysis workflow. The top row
        defines the groups for the different data levels and reduction steps
        from raw gamma-like events on the left, to high level science products
        on the right. The direction of the data flow is illustrated with the
        grey arrows. The gray folder icons represent the different sub-packages
        in \gammapy and their names. Below each icon there is a list of the most
        important objects defined in the sub-package.
    }
	\label{fig:data_flow}
\end{figure*}
%
The \gammapy package is structured into multiple sub-packages. The definition
of the content of the different sub-packages follows mostly the stages in the
data reduction workflow described in the previous section. Sub-packages
either contain data structures representing data at different data reduction
levels or contain algorithms to transition between the different data reduction
levels.

Figure~\ref{fig:data_flow} shows an overview of the different sub-packages and
their relation to each other. The \code{gammapy.data} and \code{gammapy.irf}
sub-packages define data objects to represent DL3 data, such as
event lists and instrument response functions as well as functionality
to the DL3 data from disk into memory. The \code{gammapy.makers} sub-package
contains the functionality to reduce the DL3 data to binned maps.
Binned maps and datasets, which represent a collection of binned
maps are defined in the \code{gammapy.maps} and \code{gammapy.datasets}
sub-packages respectively. Parametric models, which are defined in
\code{gammapy.modeling}, are used to jointly model a combination
of datasets for example to create source catalogs. Estimator classes,
which are contained in \code{gammapy.estinators} are used to
compute higher level science products such as flux and signficance maps,
light curves or flux points. Finally there is a \code{gammapy.analysis}
sub-package which provides a high level interface for executing analyses
defined from configuration files. In the following sections we will
introduce all sub-packages and their functionality in more detail.

\input{text/2-package-subsections/data}
\input{text/2-package-subsections/irf}
\input{text/2-package-subsections/maps}
\input{text/2-package-subsections/datasets}
\input{text/2-package-subsections/makers}
\input{text/2-package-subsections/modeling}
\input{text/2-package-subsections/estimators}
\input{text/2-package-subsections/analysis}
\input{text/2-package-subsections/stats}
\input{text/2-package-subsections/visualisation}
\input{text/2-package-subsections/astro}
\input{text/2-package-subsections/catalog}
%\input{text/2-package-subsections/utils}
